---
name: Irene
surname: Rodríguez
position: "PhD Candidate"
address: "Department of Political and Social Sciences, Universitat Pompeu Fabra, Barcelona"
phone: +34 636 600 144
www: irenerodriguezlopez.github.io
email: "irene.rodriguez@upf.edu"
twitter: irewrl
github: irenerodriguez
linkedin: IreneRodriguezL
headcolor: "414141"
date: "`r format(Sys.time(), '%B %Y')`"
output: 
  vitae::awesomecv:
    keep_tex: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(tidyverse)
library(tibble)
```

# Current position

```{r current_position}
tribble(~What, ~ When, ~ With, ~ Where, ~ Why,
        "Universitat Pompeu Fabra", "2022 - Present", "PhD Student in Political Science", "Barcelona, Spain", c("Thesis Project Title: Are we better? COVID-19 Pandemic effects on political attitudes and behavior.", "Supervisor: Dr. Toni Rodon.")) %>%
  detailed_entries(What, When, With, Where, Why)
```


# Education

```{r education}
tribble(~university, ~ years, ~ degree, ~ loc, ~ details,
        "Universitat de Barcelona", "2021 - 2022", "Postgraduate Degree in Data Analysis", "Barcelona, Spain", "Expert in Data Analysis for Political Analysis and Public Administration",
        "Universitat de Barcelona", "2020 - 2022", "MSc in Political Analysis and Institutional Assessment", "Barcelona, Spain", c("Thesis Title: The entry of Vox in the Spanish political institutions and its effect on citizens' attitudes towards immigration", "Supervisor: Dr. Albert Falcó-Gimeno"),
        "Universitat de Girona", "2016 - 2020", "BA in Political Science and Administration", "Girona, Spain", "Bachelor's Thesis: Analysis of a deliberative mini-public in Madrid") %>%
  tidyr::fill(-details) %>%
  detailed_entries(university, years, degree, loc, details)
```


# Research interests

```{r}
tribble(~interests,
         "Political behavior, public attitudes, political parties and radical right parties, quantitative methods, causal inference, quasi-experimental methods") %>%
  detailed_entries(interests)
```

# Participation in projects

```{r projects}
tribble(~university, ~ years, ~ degree, ~ loc, ~ details,
        "Universitat Pompeu Fabra", "2022 - Present", "COVIDEU Project", "Volkswagen Steiftung", c("PI: Dr. Heike Klüver (Humboldt University of Berlin", "Website: www.covideu.info")) %>%
  tidyr::fill(-details) %>%
  detailed_entries(university, years, degree, loc, details)
```

# Awards and Honors

```{r awards}
tribble(~what, ~ when, ~ with, ~where, ~why,
        "Universitat Pompeu Fabra", "2022", "Best Poster Award - Second place", "Barcelona, Spain", c("PhD Programme in Political and Social Sciences Doctoral Workshop")) %>%
  tidyr::fill(-why) %>%
  detailed_entries(what, when, with, where, why)
```

# Research

### Working on {.unnumbered}

Rodríguez, I. (n.d.). *The dangers of legitimation: how the presence of an RRP in parliament can increase antiimmigration attitudes*.

<font size="10"> Rodríguez, I. (n.d.). *Has the Covid-19 pandemic made us better? The pandemic incidence and restrictions and their relationship with radical right voting*. </font>


# Teaching

```{r}
tribble(~what, ~when, ~with, ~where, ~why,
        "Universitat Pompeu Fabra", "2022", "Qualitative Methodology II (Seminars)", "Barcelona, Spain", c("BA in Political Science and Administration"),
        "Universitat Pompeu Fabra", "2022", "Crash course on R and Basic Statistics", "Barcelona, Spain", c("BA in Journalism"),
        "Universitat de Barcelona", "2021", "Seminar on radical right parties", "Barcelona, Spain", c("Universitat de l'Experiència", "Title of the seminar: Vox in the institutions. Parliamentary behavior and effects on public opinion")) %>%
  detailed_entries(what, when, with, where, why)
```

# Workshops and conferences

```{r}
tribble(~what, ~when, ~with, ~where, ~why,
        "MPSA", "2023", "(forthcoming) Midwest Political Science Association", "Chicago, US", c("Presenting: Husstle and Tussle: How the UK's Vaccine Rollout Impacted EU Attitudes in EU Countries", "Contributing authors: Rodríguez, I., Herbig, L., Rodon, T., Klüver, H., Unan, A., Krawczyk, M., and Kuhn, T.", "Paaper part of the COVIDEU Project"),
        "RECSM Summer Methods School", "July 2022", "Big Data: Computational Analysis of Text", "Barcelona, Spain", c("Universitat Pompeu Fabra", "Instructor: Carlos Arcila (Universidad de Salamanca)"),
        "RECSM Summer Methods School", "July 2022", "Multilevel I: Introduction to Multilevel Models", "Barcelona, Spain", c("Universitat Pompeu Fabra", "Instructors: Carla Rampichini and Leonardo Grilli (Università di Firenze"),
        "Universitat Pompeu Fabra", "June 2022", "VI PhD Workshop on Empirical Research", "Barcelona, Spain", c("Organizer: Dr. Toni Rodon"),
        "Universiteit van Amsterdam", "June 2022", "I COVIDEU Project Workshop", "Amsterdam, NL", c("First workshop of the COVIDEU Project"),
        "Universitat Pompeu Fabra", "March 2022", "Doctoral Workshop", "Barcelona, Spain", c("UPhD Programme in Political and Social Sciences"),
        "Universitat Pompeu Fabra", "February 2022", "Working with Concepts in the Social Sciences", "Barcelona, Spain", c("PhD Programme in Political and Social Sciences", "Instructor: Frederic Schaffer (University of Massachussets)")) %>%
  detailed_entries(what, when, with, where, why)
```

# Skills

## Programming and language skills

\begin{cvskills}
  \cvskill
    {Programming}
    {R (Expert in Data Science)}
  \cvskill
    {Markup}
    {Markdown/Rmarkdown, LaTeX}
  \cvskill
    {Natural}
    {Spanish (native), Catalan (native), English (proficient), German (basic)}
\end{cvskills}

## Research skills

\begin{cvskills}
  \cvskill
    {Quantitative Research}
    {Regressions, quasi-experiments, natural experiments, DiD, RDD}
  \cvskill
    {Reproducible Research}
    {GitHub, GitHub Desktop}
\end{cvskills}
